\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-28 OaklandSubmission/intro.tex
comments

This paper presents \tool\footnote{Read as ``easy peasy'',
stands for Easy 2 Party Computation.}, a new \mpc framework.
\tool is the first
``cryptographic-cost aware'' framework that generates efficient and
scalable \mpc protocols from high-level programs devoid of any
cryptographic details. The generated protocols comprise combinations
of arithmetic and boolean circuits and have performance comparable to
or better than the custom, specialized
protocols from previous work (up to a factor of 19x in our experiments, depending on the functionality) \nc{I added this but I guess we are saying it many times, but might be nice to highlight perf early no?}. Below we describe the
salient features of \tool.

@@

The rest of the paper is structured as follows. We formalize \tool and
prove its correctness and security theorems in
Section~\ref{sec:ld}. Section~\ref{sec:pipe} details our partitioning
scheme and proves its security. Section~\ref{sec:impl}
presents the implementation details, and
Section~\ref{sec:eval} present a comprehensive evaluation of \tool. We
begin with an overview of \tool through an example in Section~\ref{sec:ex}. \nc{provided a pointer to sec 2 as well.}

>>>>

This paper presents \tool\footnote{Read as ``easy peasy'',
stands for Easy 2 Party Computation.}, a new \mpc framework.
\tool is the first
``cryptographic-cost aware'' framework that generates efficient and
scalable \mpc protocols from high-level programs devoid of any
cryptographic details. The generated protocols comprise combinations
of arithmetic and boolean circuits and have performance comparable to
or better than the custom, specialized
protocols from previous work (up to a factor of 19x in our
experiments, depending on the functionality) \nc{I added this but I
  guess we are saying it many times, but might be nice to highlight
  perf early no?} \aseem{My rationale was to save the numbers for
  Evaluation summary and remain high-level here.} Below we describe
the salient features of \tool.

@@

The rest of the paper is structured as follows. We formalize \tool and
prove its correctness and security theorems in
Section~\ref{sec:ld}. Section~\ref{sec:pipe} details our partitioning
scheme and proves its security. Section~\ref{sec:impl}
presents the implementation details, and
Section~\ref{sec:eval} present a comprehensive evaluation of \tool. We
begin with an overview of \tool through an example in
Section~\ref{sec:ex}. \nc{provided a pointer to sec 2 as well.}
\aseem{Sure :), I did not add it because Sec. 2 was just next line, so
  I thought it did not need a pointer.}
